Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-22 ms.tex
tdm edit

\change{During the sampling process, we fit for galactic
extinction as one of our physical parameters.
%For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
%along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the
%\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
%COBE/DIRBE and IRAS/ISSA.
%The NED database returns the extinction in all relevant bandpasses except those used by
%WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
We include the WISE bandpasses by applying the relative extinction values between
SDSS, 2MASS, and WISE calculated by \citet{Davenport14}.
In each step of our fitting process, we draw a value for $A_V$, calculate the expected extinction
in all bandpasses $A_X$ assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}, 
and then measure the likelihood of our model stellar fit to the observed apparent magnitudes.
We apply a uniform prior ranging from zero to a maximum extinction value of 0.2 
(a conservative upper limit for a field at such high Galactic latitude), and
marginalize over extinction in our final determination of stellar parameters.}

>>>>

\change{During the sampling process, we fit for galactic
extinction as one of our physical parameters.
%For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
%along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the
%\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
%COBE/DIRBE and IRAS/ISSA.
%The NED database returns the extinction in all relevant bandpasses except those used by
%WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
We include the WISE bandpasses by applying the relative extinction values between
SDSS, 2MASS, and WISE calculated by \citet{Davenport14}.
In each step of our fitting process, we draw a value for $A_V$, calculate the expected extinction
in all bandpasses $A_X$ assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}, 
and then measure the likelihood of our model stellar fit to the observed apparent magnitudes.
We apply a uniform prior ranging from zero to a maximum extinction value of 0.2 
(a generous upper limit for a field at such high Galactic latitude), and
marginalize over extinction in our final determination of stellar parameters.}
